Learning constraints in spreadsheets and tabular data

### 2016-06-12 Paper/ECAI/tabular.tex
Fixed row / column mistake
added a link to the github repository

\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[numbers]{natbib}
\usepackage{notoccite}
\usepackage{fixltx2e}
\usepackage{framed}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage[margin=0.1cm]{subcaption}
\usepackage[inline]{enumitem}

@@

A row or a column is \textbf{type-consistent} if all cells in that row or column are of the same base type, i.e. numeric or textual.
We will use notation $T[a,{:}]$ to refer to the $a$-th row of table $T$ and similarly $T[{:},a]$ for the $a$-th column.
For example, in Figure~\ref{fig:main_example}, $T_1[1,:] = [1,2,3,4]$ and $T_3[:,1] = ['$Diana Coolen$', 5]$.
$T_3[1, :]$ is not type-consistent while $T_1[:, 1]$ is.
%We will write \textbf{vector} to refer to a single row or column when its orientation does not matter.

@@

\paragraph{Visual}
The above assumptions do not hold for many tables. However, since the specification of tables is usually easy for humans, we propose a second approach which allows users to indicate tables using a visual tool.
Users select tables excluding the header and optionally specify an orientation.
The tool then generates the specification of the tables automatically.

@@

\subsection{Method}
\label{sec:evalualtion:method}
In order to obtain a benchmark of spreadsheets we looked at three sources:
1)~spreadsheets from an exercise session for teaching Excel based on~\cite{excel_book}; 2)~spreadsheets from tutorials online; and 3)~publicly available \textit{data} spreadsheets such as real-world crime statistics or financial reports\footnote{(benchmark attached to to the submitted paper)}.
All spreadsheets were converted to CSV and the table definitions are fixed.
Group definitions are only specified if the spreadsheet contains ambiguous \textit{None} values.

>>>>

\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[numbers]{natbib}
\usepackage{notoccite}
\usepackage{fixltx2e}
\usepackage{framed}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage[margin=0.1cm]{subcaption}
\usepackage[inline]{enumitem}
\usepackage{footmisc}

@@

A row or a column is \textbf{type-consistent} if all cells in that row or column are of the same base type, i.e. numeric or textual.
We will use notation $T[a,{:}]$ to refer to the $a$-th row of table $T$ and similarly $T[{:},a]$ for the $a$-th column.
For example, in Figure~\ref{fig:main_example}, $T_1[:,1] = [1,2,3,4]$ and $T_3[1,:] = ['$Diana Coolen$', 5]$.
$T_3[1, :]$ is not type-consistent while $T_1[:, 1]$ is.
%We will write \textbf{vector} to refer to a single row or column when its orientation does not matter.

@@

\paragraph{Visual}
The above assumptions do not hold for many tables. However, since the specification of tables is usually easy for humans, we propose a second approach which allows users to indicate tables using a visual tool (screenshots are available in the accompanying github repository\footnote{\url{https://github.com/for-DSAA2016-review/TaCLe}\label{github-link}}).
Users select tables excluding the header and optionally specify an orientation.
The tool then generates the specification of the tables automatically.

@@

\subsection{Method}
\label{sec:evalualtion:method}
In order to obtain a benchmark of spreadsheets we looked at three sources:
1)~spreadsheets from an exercise session for teaching Excel based on~\cite{excel_book}; 2)~spreadsheets from tutorials online; and 3)~publicly available \textit{data} spreadsheets such as real-world crime statistics or financial reports\footref{github-link}.
All spreadsheets were converted to CSV and the table definitions are fixed.
Group definitions are only specified if the spreadsheet contains ambiguous \textit{None} values.
